Databrary: A digital data library for sharing research video

### 2015-01-30 jcdl-15/paper.tex
Combine some sentences; Drew -> Andrew

\author{
\alignauthor
Dylan A. Simon\\
	\affaddr{Databrary Project}\\
	\affaddr{New York University}\\
	\affaddr{New York, NY, USA}\\
	\email{dylan@databrary.org}
\alignauthor
Drew Gordon\\
	\affaddr{Databrary Project}\\
	\affaddr{New York University}\\
	\affaddr{New York, NY, USA}\\
	\email{drew@databrary.org}
\alignauthor
Lisa Steiger\\
	\affaddr{Databrary Project}\\
	\affaddr{New York University}\\
	\affaddr{New York, NY, USA}\\
	\email{lisa@databrary.org}
\and
Rick O. Gilmore\\
	\affaddr{Penn State}\\
	\affaddr{Department of Psychology}\\
	\affaddr{University Park, PA, USA}\\
	\email{rogilmore@psu.edu}
}

@@

In addition to containing values, records are also used to organize sessions.
We have found that different researchers organize data files in substantially different ways.
Researchers employ different organizational structures, often depending on the primary focus of analysis for their specific study or sub-domain.
Common directory structures include participants, session date, experimental condition, phase of analysis, and age group.
Sometimes even single video files are split up into segments according to scene or activity, and researchers consider this property the primary organizational principle.

>>>>

\author{
\alignauthor
Dylan A. Simon\\
	\affaddr{Databrary Project}\\
	\affaddr{New York University}\\
	\affaddr{New York, NY, USA}\\
	\email{dylan@databrary.org}
\alignauthor
Andrew Gordon\\
	\affaddr{Databrary Project}\\
	\affaddr{New York University}\\
	\affaddr{New York, NY, USA}\\
	\email{drew@databrary.org}
\alignauthor
Lisa Steiger\\
	\affaddr{Databrary Project}\\
	\affaddr{New York University}\\
	\affaddr{New York, NY, USA}\\
	\email{lisa@databrary.org}
\and
Rick O. Gilmore\\
	\affaddr{Penn State}\\
	\affaddr{Department of Psychology}\\
	\affaddr{University Park, PA, USA}\\
	\email{rogilmore@psu.edu}
}

@@

In addition to containing values, records are also used to organize sessions.
We have found that different researchers employ substantially different organizational structures for their files depending on their needs.
Common directory structures include participants, session date, experimental condition, phase of analysis, and age group.
Sometimes even single video files are split up into segments according to scene or activity, and researchers consider this property the primary organizational principle.
